Choosing the Choice: Reflections on Modelling Decisions and Behaviour in Demographic Agent-Based Models

### 2017-03-24 article.tex

We suggest that inclusion and operationalisation of context are best tackled through an iterative process of development, and evaluation against empirical data, somewhat similar to that proposed by \cite{Cioffi-Revilla2010}. This approach places considerable demands on the modeller in terms of developing the model, but also in exercising their judgement as to what should be included, and identifying where a component should be iterated out. In a sense, this is a similar process to the stepwise approaches commonly used in constructing regression models. Here, however, it is considerably less amenable to automation, both because augmenting a model is time consuming, and because evaluating complex models poses considerable challenges. The challenge of evaluation can be somewhat ameliorated by the use of techniques like sensitivity analysis (see \citet{Thiele2014} for a review of several techniques, and \citet{Oakley2004} for an alternative approach), which can support the modeller in identifying how the individual parameters of a model contribute to overall outputs. This too has limitations, because as we discuss later in relation to heterogeneity in agents (section \ref{heterogeneity-in-decision-strategies}), context can take the form of both process, and parameter.
As a result, the onus remains on the modeller to use their best judgement.

>>>>

We suggest that inclusion and operationalisation of context are best tackled through an iterative process of development, and evaluation against empirical data, somewhat similar to that proposed by \cite{Cioffi-Revilla2010}. This approach places considerable demands on the modeller in terms of developing the model, but also in exercising their judgement as to what should be included, and identifying where a component should be iterated out. This is however an expensive exercise, both because augmenting a model is time consuming, and because evaluating complex models poses considerable challenges. The challenge of evaluation can be somewhat ameliorated by the use of techniques like sensitivity analysis (see \citet{Thiele2014} for a review of several techniques, and \citet{Oakley2004} for an alternative approach), which can support the modeller in identifying how the individual parameters of a model contribute to overall outputs. A key benefit to this is that parameters which do not significantly impact the results of a model can be removed. This too has limitations, because as we discuss later in relation to heterogeneity in agents (section \ref{heterogeneity-in-decision-strategies}), context can take the form of both process, and parameter, and sensitivity analysis is directly informative only about the latter.
As a result, the onus remains on the modeller to use their best judgement.
